### 2023-02-01 README.Rmd
check URLs

<!-- badges: start -->
[![rOpenSci Badge](https://badges.ropensci.org/87_status.svg)](https://github.com/ropensci/software-review/issues/87)[![JOSS status](https://joss.theoj.org/papers/10.21105/joss.00355/status.svg)](https://joss.theoj.org/papers/10.21105/joss.00355)[![DOI](https://zenodo.org/badge/50553382.svg)](https://zenodo.org/badge/latestdoi/50553382)[![R-CMD-check](https://github.com/ropensci/visdat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ropensci/visdat/actions/workflows/R-CMD-check.yaml)[![Codecov test coverage](https://codecov.io/gh/ropensci/visdat/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/visdat?branch=master)[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/visdat)](https://cran.r-project.org/package=visdat)[![CRAN Logs](http://cranlogs.r-pkg.org/badges/visdat)](https://CRAN.R-project.org/package=visdat)[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/)
<!-- badges: end -->

@@

You can read more about visdat in the vignette, ["using visdat"](http://visdat.njtierney.com/articles/using_visdat.html).

>>>>

<!-- badges: start -->
[![rOpenSci Badge](https://badges.ropensci.org/87_status.svg)](https://github.com/ropensci/software-review/issues/87)[![JOSS status](https://joss.theoj.org/papers/10.21105/joss.00355/status.svg)](https://joss.theoj.org/papers/10.21105/joss.00355)[![DOI](https://zenodo.org/badge/50553382.svg)](https://zenodo.org/badge/latestdoi/50553382)[![R-CMD-check](https://github.com/ropensci/visdat/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ropensci/visdat/actions/workflows/R-CMD-check.yaml)[![Codecov test coverage](https://codecov.io/gh/ropensci/visdat/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ropensci/visdat?branch=master)[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/visdat)](https://cran.r-project.org/package=visdat)[![CRAN Logs](http://cranlogs.r-pkg.org/badges/visdat)](https://CRAN.R-project.org/package=visdat)[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/)
<!-- badges: end -->

@@

You can read more about visdat in the vignette, ["using visdat"]https://docs.ropensci.org/visdat/articles/using_visdat.html).
